The transition redshift as a probe of reionization

### 2019-08-27 paper/ms.tex
Slight update to text

This cross-correlation was first studied with the CO rotational lines
\citep{2011ApJ...741...70L}, and then the [\CII] \citep{2012ApJ...745...49G}
and Ly$\alpha$ lines \citep{2013ApJ...763..132S}. The possibility of using the
cross-bispectrum the 21~cm and [\CII] fields has been explored
\citep{2018ApJ...867...26B}, along with combining the three cross-spectra with
a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. While in
this work we will only consider the cross-correlation between 21~cm and
galaxies, all of what we consider is applicable to the transition redshift as
computed by cross-correlating 21~cm with any of these emission lines.

>>>>

This cross-correlation was first studied with the CO rotational lines
\citep{2011ApJ...741...70L}, and then the [\CII] \citep{2012ApJ...745...49G}
and Ly$\alpha$ lines \citep{2013ApJ...763..132S}. The possibility of using the
cross-bispectrum the 21~cm and [\CII] fields has been explored
\citep{2018ApJ...867...26B}, along with combining the three cross-spectra with
a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. Because the
transition redshift is typically $\z_{\star} \sim 10$, it is unclear how much
metal enrichment will have occurred by this early time.
